Understanding the impacts of video-guided activities on parent-child interaction

### 2019-09-24 paper/manuscript.Rmd
updated Exp 1 exploratory regressions

In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
Parents were randomly assigned to the video condition or the control condition; parents in the _activity video_ condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video. 
Parents in the _control_ condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.

@@

### Procedure.
After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played. 
Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed. 
The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.[^2]
In the Control condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
They were not given any additional instructions about how to use the props.

@@

Parents' child-directed speech during the play sessions was transcribed.
The transcripts and hand-coded joint attention data were analyzed according to our preregistration[^3], with any deviations or extensions noted.
Below we first report the lexical diversity results, followed by the joint attention results.

@@

# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
modTTR <- stan_glmer(TTR ~ condition + age + gender + parent_ed + (1|video), data=e1ld)
summary(modTTR) # condition:Exp -0.113 t(52.4) = 4.22 p<.001
e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") #

modMTLD <- stan_glmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=e1ld)
summary(modMTLD) # condition -8.73 t(55) = 2.67 p=.001 !! singular fit, changing optimizer did not help
e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") #

# predict word tokens
tokens_mod <- stan_glmer(tokens ~ condition + age + gender + parent_ed + (1|video),  data=e1ld) 
summary(tokens_mod)
get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 55.7

# follow-up on EPAQ
tokens_modEPAQ <- stan_glmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1|video),  data=e1ld) # only 54 parents completed the EPAQ
summary(tokens_modEPAQ) # condition 56.02 t(40.4) = 2.30 p<.05
e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 54.8

# predict word types
types_mod <- stan_glmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=e1ld) 
summary(types_mod) # nothing

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), gender, and parent's education level with a random intercept per video using rstanarm [@rstanarm]. 
For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 95% Bayesian credible intervals (95% CI), demarcating the range within which 95% of the posterior predictive values fall.
There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]). 
There were no significant effects of age, gender, or parent's level of education.
A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no other significant effects.
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

@@

We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`])), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).

@@

model_string = "~ Condition * age + (1| Video)" # + gender + parent_ed
# Total number of bids
e1bids_mod <- stan_glmer(paste("bids_tot", model_string), data = e1ja) # 
summary(e1bids_mod) # condition beta = 2.6, t(40.3) = 2.95 p<.01, gender p=.05 ?
e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video")

@@

e1tja_mod <- stan_lmer(paste("total_ja", model_string), data = e1ja)
summary(e1tja_mod) # NA
e1tjadur_mod <- stan_lmer(paste("total_lja", model_string), control = list(adapt_delta = 0.99), data = e1ja)
summary(e1tjadur_mod) #

# Episodes of passive joint attention.
e1pja_mod <- stan_lmer(paste("pja", model_string), data = e1ja)
summary(e1pja_mod) # NA
# Episodes of coordinated joint attention.
e1cja_mod <- stan_lmer(paste("cja", model_string), control = list(adapt_delta = 0.99), data = e1ja) 
summary(e1cja_mod) # NA

# Total duration of passive joint attention.
e1pja_time_mod <- stan_lmer(paste("pja_length", model_string), data = e1ja)
summary(e1pja_time_mod) # NA
# Total duration of coordinated joint attention.
e1cja_time_mod <- stan_lmer(paste("cja_length", model_string), data = e1ja)
summary(e1cja_time_mod) # NA
```

```{r e1ja-epaq-regressions, include=F, echo=F}
# follow-up regression (if we find a sig effect?)
model_string =  "~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed + (1| Video)"

# Total number of bids
e1bids_mod <- stan_glmer(paste("bids_tot", model_string), data = e1ja) # 1 divergent transitions after warmup. Increasing adapt_delta above 0.95 may help
summary(e1bids_mod) # condition beta = 3.51, t(40.3) = 2.95 p<.01, gender p=.05 ?
e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video")

# Episodes of coordinated joint attention.
e1cja_mod <- stan_lmer(paste("cja", model_string), data = e1ja)
summary(e1cja_mod) # NA

# Episodes of passive joint attention.
e1pja_mod <- stan_lmer(paste("pja", model_string), data = e1ja)
summary(e1pja_mod) # condition*RR beta=1.8 Bayes 95% Ci = [.1,3.5]
e1pja = get_stan_glmer_reporting_values(e1pja_mod, "ConditionActivity Video:RR")

@@

We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. 
This model included random intercepts per video. 
There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]).

Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes. 
For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=`r e1pja["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pja['95pLB']`,`r e1pja['95pUB']`]), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
Figure \@ref(fig:JA) (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.

@@

In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more. 
Looking at the most frequent content words parents used after the Activity Video, ...
In contrast, the most frequent content words parents used in the Control condition were...

@@

In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
There was also a significant main effect of age ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`,`r e2tjaAge["95pUB"]`]), showing that the number of episodes of JA decreased with the child's age. 
However, a significant interaction of age and condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:JA} (right bottom), demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.

@@

This work was supported by a gift from Kinedu, Inc. 
Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion.

>>>>

In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
Parents were randomly assigned to one of two conditions: parents in the _Activity Video_ condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video. 
Parents in the _No Video_ condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.

@@

### Procedure.
After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played. 
Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed. 
The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.[^2]
In the No Video condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
They were not given any additional instructions about how to use the props.

@@

Parents' child-directed speech during the play sessions was transcribed.
The transcripts and hand-coded joint attention data were analyzed according to our preregistration[^3], with any deviations or exploratory analyses noted.
Below we first report the lexical diversity results, followed by the joint attention results.

@@

modTTR <- stan_glmer(TTR ~ condition * age + (1|video), data=e1ld)
summary(modTTR) 
e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.11

modMTLD <- stan_glmer(MTLD ~ condition * age + (1|video), data=e1ld)
summary(modMTLD) 
e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") # -9.19

# predict word tokens
tokens_mod <- stan_glmer(tokens ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld) 
summary(tokens_mod)
e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 59.41

# predict word types
types_mod <- stan_glmer(types ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld)
summary(types_mod) # nothing

@@

```{r, e1ld-exploratory, echo=F, include=F}
# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
e1model_string = "~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video)"
# only 54 parents completed the EPAQ
modTTRE <- stan_glmer(paste("TTR", e1model_string), data=e1ld)
summary(modTTRE) #

modMTLDE <- stan_glmer(paste("MTLD", e1model_string), data=e1ld)
summary(modMTLDE) #

tokens_modE <- stan_glmer(paste("tokens", e1model_string),  data=e1ld) 
summary(tokens_modE) # condition 54.4

# predict word types
types_modE <- stan_glmer(paste("types", e1model_string), data=e1ld) 
summary(types_modE) # 
```

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 95% Bayesian credible intervals (95% CI), demarcating the range within which 95% of the posterior predictive values fall.
There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]). 
There were no significant effects of age, gender, or parent's level of education.
A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no other significant effects.
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

@@

We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`])), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).

@@

model_string = "~ Condition * age + (1| Video)" # + gender + parent_ed
# Total number of bids
e1bids_mod <- stan_glmer(paste("bids_tot", model_string), data = e1ja) # 
summary(e1bids_mod) 
e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video") # 2.59

@@

e1tja_mod <- stan_lmer(paste("total_ja", model_string), data = e1ja)
summary(e1tja_mod) # NA

e1tjadur_mod <- stan_lmer(paste("total_lja", model_string), control = list(adapt_delta = 0.99), data = e1ja)
summary(e1tjadur_mod) # NA

# Episodes of passive joint attention.
e1pja_mod <- stan_lmer(paste("pja", model_string), data = e1ja)
summary(e1pja_mod) # NA

# Episodes of coordinated joint attention.
e1cja_mod <- stan_lmer(paste("cja", model_string), control = list(adapt_delta = 0.99), data = e1ja) 
summary(e1cja_mod) # NA

@@

```{r e1ja-epaq-regressions, include=F, echo=F}
# follow-up regression (if we find a sig effect?)
model_stringE =  "~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed + (1| Video)"

# Total number of bids
e1bids_modE <- stan_glmer(paste("bids_tot", model_stringE), data = e1ja) 
summary(e1bids_modE) # cond, gender close

# Episodes of coordinated joint attention.
e1cja_modE <- stan_lmer(paste("cja", model_stringE), data = e1ja)
summary(e1cja_modE) # NA

# Episodes of passive joint attention.
e1pja_modE <- stan_lmer(paste("pja", model_stringE), data = e1ja)
summary(e1pja_modE) # condition*RR beta=1.8, RR close
get_stan_glmer_reporting_values(e1pja_modE, "RR") # -1.08, 95% CI = [-2.18,0.07]
e1pjaE = get_stan_glmer_reporting_values(e1pja_modE, "ConditionActivity Video:RR")

# Total duration of passive joint attention.
e1pja_time_modE <- stan_lmer(paste("pja_length", model_stringE), data = e1ja)
summary(e1pja_time_modE) # NA

# Total duration of coordinated joint attention.
e1cja_time_modE <- stan_lmer(paste("cja_length", model_stringE), data = e1ja)
summary(e1cja_time_modE) # NA
```

We fit a Bayesian mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video. 
There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]). 
Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
There were no significant effects on the number of or total duration of coordinated or passive JA episodes.
Figure \@ref(fig:JA) (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. 
These models included random intercepts per video. 
Of these exploratory regressions, only the regression predicting the number of passive JA episodes produced a significant effect involving these demographic variables: an interaction of condition and RR ($\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaE['95pLB']`,`r e1pjaE['95pUB']`]), shows that for parents in the Activity Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.

@@

In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more. 
Looking at the most frequent content words parents used after the Activity Video, ...
In contrast, the most frequent content words parents used in the No Video condition were...

@@

In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
There was also a significant main effect of age ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`,`r e2tjaAge["95pUB"]`]), showing that the number of episodes of JA decreased with the child's age. 
However, a significant interaction of age and condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:JA} (right bottom), demonstrates that there were more episodes of JA for older children in the Activity Video condition (comparable to episodes of JA for younger children).

@@

This work was supported by a gift and a contract from Kinedu, Inc. to the Language and Cognition Lab. 
Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion.

### 2019-09-24 paper/manuscript.tex
updated Exp 1 exploratory regressions

In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
Parents were randomly assigned to the video condition or the control condition; parents in the \emph{activity video} condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
Parents in the \emph{control} condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.

@@

After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played.
Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed.
The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.\footnote{Based on piloting, we estimated these activities would would only require three minutes to complete.}
In the Control condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes.
They were not given any additional instructions about how to use the props.

@@

Parents' child-directed speech during the play sessions was transcribed.
The transcripts and hand-coded joint attention data were analyzed according to our preregistration\footnote{Preregistration: \url{https://osf.io/2bpdf/}{]}}, with any deviations or extensions noted.
Below we first report the lexical diversity results, followed by the joint attention results.

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), gender, and parent's education level with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 95\% Bayesian credible intervals (95\% CI), demarcating the range within which 95\% of the posterior predictive values fall.
There was significantly lower TTR in the Video condition (mean: 0.32) than in the Control condition (mean: 0.43, \(\beta=\)-0.11, 95\% CI={[}-0.16,-0.06{]}).
There were no significant effects of age, gender, or parent's level of education.
A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: 17.87) than in the Control condition (mean: 27.09, \(\beta=\)-8.62, 95\% CI={[}-15.15,-2.01{]}), with no other significant effects.
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta=\) 56.36, 95\% CI={[}14.02,96.32{]})), with parents using more words in the Video condition (mean: 225, bootstrapped 95\% confidence intervals (CI): {[}199,252{]}) than in the Control condition (mean: 165, bootstrapped 95\% CI: {[}139,193{]}).

@@

We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
This model included random intercepts per video.
There were significantly more bids for JA in the Video condition (mean: 6.30, sd: 2.76) than in the Control condition (mean: 3.73, sd: 2.74, \(\beta=3.40\), 95\% CI={[}1.03,5.73{]}).

Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes.
For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR (\(\beta=1.82\), 95\% CI={[}0.20,3.48{]}), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
Figure \ref{fig:JA} (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.

@@

In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more.
Looking at the most frequent content words parents used after the Activity Video, \ldots{}
In contrast, the most frequent content words parents used in the Control condition were\ldots{}

@@

In the regression predicting the number of episodes of JA, there was a significant main effect of condition (\(\beta=1.48\), 95\% CI = {[}0.15,2.78{]}), with more episodes of JA occurring after the Activity Video (mean: 8.80, 95\% CI: {[}7.97, 9.63{]}) than after the Control Video (mean: 7.33, 95\% CI: {[}6.58, 8.11{]}).
There was also a significant main effect of age (\(\beta=-5\), 95\% CI = {[}-8.27,-1.41{]}), showing that the number of episodes of JA decreased with the child's age.
However, a significant interaction of age and condition (\(\beta=5.60\), 95\% CI = {[}0.46,10.37{]}), shown in Figure \ref{fig:JA} (right bottom), demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.

@@

This work was supported by a gift from Kinedu, Inc.
Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion.

>>>>

In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
Parents were randomly assigned to one of two conditions: parents in the \emph{Activity Video} condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
Parents in the \emph{No Video} condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.

@@

After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played.
Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed.
The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.\footnote{Based on piloting, we estimated these activities would would only require three minutes to complete.}
In the No Video condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes.
They were not given any additional instructions about how to use the props.

@@

Parents' child-directed speech during the play sessions was transcribed.
The transcripts and hand-coded joint attention data were analyzed according to our preregistration\footnote{Preregistration: \url{https://osf.io/2bpdf/}{]}}, with any deviations or exploratory analyses noted.
Below we first report the lexical diversity results, followed by the joint attention results.

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 95\% Bayesian credible intervals (95\% CI), demarcating the range within which 95\% of the posterior predictive values fall.
There was significantly lower TTR in the Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 95\% CI={[}-0.16,-0.06{]}).
There were no significant effects of age, gender, or parent's level of education.
A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-9.30, 95\% CI={[}-15.37,-3.18{]}), with no other significant effects.
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta=\) 59.07, 95\% CI={[}19.58,97.44{]})), with parents using more words in the Activity Video condition (mean: 225, bootstrapped 95\% confidence intervals (CI): {[}199,252{]}) than in the No Video condition (mean: 165, bootstrapped 95\% CI: {[}139,193{]}).

@@

We fit a Bayesian mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
There were significantly more bids for JA in the Video condition (mean: 6.30, sd: 2.76) than in the No Video condition (mean: 3.73, sd: 2.74, \(\beta=2.56\), 95\% CI={[}0.74,4.44{]}).
Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
There were no significant effects on the number of or total duration of coordinated or passive JA episodes.
Figure \ref{fig:JA} (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
These models included random intercepts per video.
Of these exploratory regressions, only the regression predicting the number of passive JA episodes produced a significant effect involving these demographic variables: an interaction of condition and RR (\(\beta=1.82\), 95\% CI={[}0.20,3.48{]}), shows that for parents in the Activity Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.

@@

In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more.
Looking at the most frequent content words parents used after the Activity Video, \ldots{}
In contrast, the most frequent content words parents used in the No Video condition were\ldots{}

@@

In the regression predicting the number of episodes of JA, there was a significant main effect of condition (\(\beta=1.48\), 95\% CI = {[}0.15,2.78{]}), with more episodes of JA occurring after the Activity Video (mean: 8.80, 95\% CI: {[}7.97, 9.63{]}) than after the Control Video (mean: 7.33, 95\% CI: {[}6.58, 8.11{]}).
There was also a significant main effect of age (\(\beta=-5\), 95\% CI = {[}-8.27,-1.41{]}), showing that the number of episodes of JA decreased with the child's age.
However, a significant interaction of age and condition (\(\beta=5.60\), 95\% CI = {[}0.46,10.37{]}), shown in Figure \ref{fig:JA} (right bottom), demonstrates that there were more episodes of JA for older children in the Activity Video condition (comparable to episodes of JA for younger children).

\hypertarget{exploratory-analyses-1}{%
\subsubsection{Exploratory Analyses}\label{exploratory-analyses-1}}

@@

This work was supported by a gift and a contract from Kinedu, Inc.~to the Language and Cognition Lab.
Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion.
